Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2024-02-13 outputs/paper/paper.qmd
edits

```{r setup}
#| echo: false
#| message: false
#| warning: false
# install.packages('readr')
# install.packages('here')
# install.packages("readstata13")  #  readstata13_0.9.2
# install.packages("MASS") # MASS_7.3-51.6  
# install.packages("sandwich")  # sandwich_2.5-1 
# install.packages("lmtest") # lmtest_0.9-37 
# install.packages("pBrackets") # pBrackets_1.0  
# install.packages("dplyr") 
# install.packages("tidyverse")
# install.packages("list)
# install.packages("knitr")
# install.packages("kableExtra")

@@

```{r}
#| label: fig-collection
#| fig-cap: "00000000000000000000000000000000000000000000000000000000000000000000000000"
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: fig-collection
#| fig-cap: "000000000000000000000000000000000000000000000000000000000000"
#| echo: false
#| message: false
#| warning: false

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ # 
######## B. META-ANALYSIS: for each of the hypotheses ######## 
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #

# Data preparation: Split dataset in 3 based on outcome type
# 1) outgroup dataset
dat_outgroup <- dat[dat$PA_Category == 10 |
                      dat$PA_Category == 99, ]
length(unique(dat_outgroup$ID_R))#number of manuscripts (N_j)
# 2) conservative shift dataset
dat_conservatism <- dat[dat$PA_Category == 5 |
                          dat$PA_Category == 6 |
                          dat$PA_Category == 7 |
                          dat$PA_Category == 8 |
                          dat$PA_Category == 9 |
                          dat$PA_Category == 11, ]
length(unique(dat_conservatism$ID_R))#number of manuscripts (N_j)
# 3) rally-around-the-flag dataset
dat_rally <- dat[dat$PA_Category == 1 |
                   dat$PA_Category == 2 |
                   dat$PA_Category == 3 |
                   dat$PA_Category == 4, ]
length(unique(dat_rally$ID_R))#number of manuscripts (N_j)
# double check (total number of effect sizes; N_k)
count(dat_outgroup) + count(dat_conservatism) + count(dat_rally)

##### 1. Fit empty 3-level model using the meta3 function #####

### To replicate Table 2: call summary() function for each of outcome cluster
      ## coef(model...)[1] = Fishers' Z correlation coefficients (Zr)
### To replicate the correlation coefficients mentioned in the text, 
### call the FisherZinv() function for each outcome cluster.

# Outgroup hostility (Table 2)
set.seed(1234)
model_og_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                       data = dat_outgroup, 
                       I2=c("I2q", "ICC"),
                       intervals.type = "LB",
                       model.name = "3 level outgroup LB")
summary(model_og_LBCI)#results presented in Table 2, as well as
#throughout the Supplementary Information (esp. Table B.3).
FisherZInv(coef(model_og_LBCI)[1])#rho reported in text

# Conservative shift (Table 2)
set.seed(1234)
model_cs_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                       data = dat_conservatism, 
                       I2=c("I2q", "ICC"),
                       intervals.type = "LB",
                       model.name = "3 level conservatism LB")
summary(model_cs_LBCI)#results presented in Table 2, as well as
#throughout the Supplementary Information (esp. Table B.3).
FisherZInv(coef(model_cs_LBCI)[1])#rho reported in text

# Rally-around-the-flag (Table 2)
set.seed(1234)
model_rf_LBCI <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                       data = dat_rally, 
                       I2=c("I2q", "ICC"),
                       intervals.type = "LB",
                       model.name = "3 level rally LB")
summary(model_rf_LBCI)#results presented in Table 2, as well as
#throughout the Supplementary Information (esp. Table B.3).
FisherZInv(coef(model_rf_LBCI)[1])#rho reported in text

## Substantive interpretation --------------------------------------------------
## i.e., comparison to 2016 ANES Feeling Thermometers
anes2016 <- read_dta(file = "/cloud/project/raw/data/anes_timeseries_2016.dta")
#select variables to summarize
anes2016 <- anes2016 %>%
  select(immterm = V162313, 
         reptherm = V161096) 
#format(round(psych::describe(anes2016),3), nsmall=3): counts NA's
#recode NA's (!)
anes2016$immterm <- ifelse(anes2016$immterm %in% -9:-1, NA, 
                           identity(anes2016$immterm)) 
anes2016$reptherm <- ifelse(anes2016$reptherm %in% -99:-1, NA, 
                            identity(anes2016$reptherm))
#find correct SDs to use in calculations based on Paluck et al. (2021)
format(round(psych::describe(anes2016),3), nsmall=3) 
#the effect of terror on the feeling therm. toward immigrants. 6.9
cohens_d(r = FisherZInv(coef(model_og_LBCI)[1]))*27.285 
#the effect of terror on the feeling therm. toward Rep. party: 7.2
cohens_d(r = FisherZInv(coef(model_cs_LBCI)[1]))*27.330

## Practical implication -------------------------------------------------------
## i.e., what sample size is recommended based on this meta-analysis?
# Outgroup hostility
pwr.r.test(r = FisherZInv(coef(model_og_LBCI)[1]), sig.level = 0.05, power = 0.8) 
# Conservative shift
pwr.r.test(r = FisherZInv(coef(model_cs_LBCI)[1]), sig.level = 0.05, power = 0.8) 
# Rally-around-the-flag
pwr.r.test(r = FisherZInv(coef(model_rf_LBCI)[1]), sig.level = 0.05, power = 0.8)

##### 2. Test variance components #####

### Note: These results are briefly mentioned in footnote 13, but 
### full results are discussed and presented in SI B.2.3.

# Outgroup hostility

#tau^2_3=0 (reported in Table B.2)
set.seed(1234)
model_og_t3 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                      data = dat_outgroup, 
                      RE3.constraints = 0, # constraining between-study level
                      model.name = "Tau2_3 eq 0",
                      intervals.type = "LB")
summary(model_og_t3)#this equals a conventional random-effects model
anova(model_og_LBCI, model_og_t3)

#tau^2_2=0 (reported in Table B.2)
set.seed(1234)
model_og_t2 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                     data = dat_outgroup,
                     RE2.constraints = 0, # constraining within-study level
                     model.name = "Tau2_2 eq 0",
                     intervals.type = "LB")
summary(model_og_t2)
anova(model_og_LBCI, model_og_t2)

# Conservative shift

#tau^2_3=0 (reported in Table B.2)
set.seed(1234)
model_cs_t3 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                     data = dat_conservatism, 
                     RE3.constraints = 0, # constraining between-study level
                     model.name = "Tau2_3 eq 0",
                     intervals.type = "LB")
summary(model_cs_t3)
anova(model_cs_LBCI, model_cs_t3)

#tau^2_2=0 (reported in Table B.2)
set.seed(1234)
model_cs_t2 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                     data = dat_conservatism,
                     RE2.constraints = 0, # constraining within-study level
                     model.name = "Tau2_2 eq 0",
                     intervals.type = "LB")
summary(model_cs_t2)
anova(model_cs_LBCI, model_cs_t2)

# Rally-around-the-flag

#tau^2_3=0 (reported in Table B.2)
set.seed(1234)
model_rf_t3 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                     data = dat_rally, 
                     RE3.constraints = 0, # constraining between-study level
                     model.name = "Tau2_3 eq 0",
                     intervals.type = "LB")
summary(model_rf_t3)
anova(model_rf_LBCI, model_rf_t3)

#tau^2_2=0 (reported in Table B.2)
set.seed(1234)
model_rf_t2 <- meta3L(y=Fisher, v=Variance_F, cluster=ID_R,
                     data = dat_rally,
                     RE2.constraints = 0, # constraining within-study level
                     model.name = "Tau2_2 eq 0",
                     intervals.type = "LB")
summary(model_rf_t2)
anova(model_rf_LBCI, model_rf_t2)

>>>>

```{r setup}
#| echo: false
#| message: false
#| warning: false
# install.packages('readr')
# install.packages('here')
# install.packages("readstata13")  #  readstata13_0.9.2
# install.packages("MASS") # MASS_7.3-51.6  
# install.packages("sandwich")  # sandwich_2.5-1 
# install.packages("lmtest") # lmtest_0.9-37 
# install.packages("pBrackets") # pBrackets_1.0  
# install.packages("dplyr") 
# install.packages("tidyverse")
# install.packages("list")
# install.packages("knitr")
# install.packages("kableExtra")

@@

```{r}
#| label: fig-collection
#| fig-cap: "Panel A displays the number of unique studies conducted over time, Panel B the number of manuscripts published over time, Panel C the frequency of used terrorism measures (in percentage), and Panel D the frequency of studied types of terrorism (in percentage)"
#| echo: false
#| message: false
#| warning: false

@@

As depicted in @fig-collection(A) and (B), scholarly interest in exploring the link between terrorism and public attitudes notably began following the 9/11 attacks, and received further impetus following the 2015–16 Islamic State (IS) attacks. Put differently, the figures imply that this research domain is significantly influenced by specific events.

Moreover, from 1985 to 2020, researchers have employed diverse methodologies to measure exposure to terrorism (refer to @fig-collection(C)). Some studies exposed participants to news articles or video clips depicting specific acts of violence (e.g., 9/11), while in other cases, exposure occurred naturally when surveys coincided with terror attacks (527 data points of acts of violence , as 30% ). Additionally, studies have assessed or manipulated individuals' perceptions of terrorism threats (threat of violence: 520 data points as 30%), examined affective responses such as fear (146 data points) and anger (111 data points), and investigated self-reported exposure to terrorism through personal experiences, relatives' experiences, or media coverage (self-reported exposure: 184 data points).

The most frequently studied acts of violence are—perhaps unsurprisingly—9/11, the Israeli-Palestinian conflict, and the 2015 series of IS attacks in Paris. Consequently, regarding the ideology behind the violence (@fig-collection(D)), the vast majority of effect sizes quantify the effects of or relationship with Islamist terrorism (1,064 data points, 61%), following by no ideology terrorism, whereas the share of information on how the public reacts to extreme-right terror is remarkably low (35 data points, 2%).

Table 1 demonstrates that...
